Gentoo Package Dependencies over Time

### 2014-08-07 Paper/paper.tex
Moved sections around

\begin{wrapfigure}{r}{0.5\textwidth}
\centering
\includegraphics[width=0.95\linewidth]{packageCountUnfiltered2.pdf}
\caption{Growth of the total number of packages in the Gentoo package database over time.}\label{fig:pkgsgrowth}
\end{wrapfigure}

\begin{wrapfigure}{r}{0.5\textwidth}
\centering
\includegraphics[width=0.95\linewidth]{packageCountDeltaUnfiltered2.pdf}
\caption{The number of package additions and removals over time.}\label{fig:pkgsgrowthdelta}
\end{wrapfigure}

@@

\begin{wrapfigure}{r}{0.5\textwidth}
\centering
\includegraphics[width=\linewidth]{histo-out.pdf}
\caption{Double logarithmic histograms of the number of dependencies per package. }\label{fig:dephisto-out}
\end{wrapfigure}

\begin{wrapfigure}{r}{0.5\textwidth}
\centering
\includegraphics[width=\linewidth]{histo-in.pdf}
\caption{Double logarithmic histograms of the number of dependers per package.}\label{fig:dephisto-in}
\end{wrapfigure}

@@

\section{the KDE Subgraph}

@@

\section{TESTING}

@@

\section{Related Work}

@@

\section{Relevance}

>>>>

\begin{figure}
\centering
\subfigure[Total number of packages]{\includegraphics[width=0.45\textwidth]{packageCountUnfiltered2.pdf}\label{fig:pkgsgrowth}}
\subfigure[Additions and removals]{\includegraphics[width=0.45\textwidth]{packageCountDeltaUnfiltered2.pdf}\label{fig:pkgsgrowthdelta}}
\caption{Growth of the Gentoo package database over time.}\label{fig:pkgsgrowth}
\end{figure}

@@

\begin{figure}
\centering
\subfigure[Dependencies per package]{\includegraphics[width=0.45\textwidth]{histo-out.pdf}\label{fig:dephisto-out}}
\subfigure[Dependers per package]{\includegraphics[width=0.45\textwidth]{histo-in.pdf}\label{fig:dephisto-in}}
\caption{Double logarithmic histograms of the number of incoming and outgoing dependencies per package.}
\end{figure}

@@

\subsection{The KDE Subgraph}

@@

\subsection{Hypothesis testing}

@@

@@

\section{Relevance — Implications to practice and research}
